% Anoop Kunjuraman - Resume https://en.wikibooks.org/wiki/LaTeX/Basics
% Template modified from https://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass[margin]{res}
\usepackage[hidelinks]{hyperref} 
\usepackage{enumitem}
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
% \usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
\moveleft.5\hoffset\centerline{\large\bf Anoop Kunjuraman}
% Draw a horizontal line the whole width of resume:
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
\moveleft.5\hoffset\centerline{Dallas, TX \quad \textbf{Phone:} (215) 285-0498 \quad \href{mailto:anoopengineer@gmail.com}{anoopengineer@gmail.com} \quad \href{https://anoop.kunjuraman.com}{https://anoop.kunjuraman.com}}

\begin{resume}
    \section{Synopsis}
    Software engineering leader with 14 years experience is creating and leading great teams.
    Proven track record in leading mission critical programs with strict budgets and regulatory controls.
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Cloud Migration \& driving cross organization technology transformation.
        \item Implementing full stack petabyte scale data centric mission critical applications.
        \item Building distributed, fault tolerant, scalable systems.
        \item Building the best team. Hiring and retaining the best talent. Diversity advocasy.
        \item Experienced in multiple domains -- embedded device programming, big data, full stack, security
        \item Loves coding -- Python, Javascript (also Go lang and Java in past)
    \end{itemize}

    \section{Education}
     {\sl Master of Science,} Software Systems, 2010 -- 2012 \\
    % \sl will be bold italic in New Century Schoolbook (or
    % any postscript font) and just slanted in
    %	Computer Modern (default) font
    Birla Institute of Technology \& Science (BITS), Pilani, India\\
    \\
    {\sl Bachelor in Technology,} Electronics \& Communication, 2002 -- 2006 \\
    University of Kerala, India \\

    \section{Patents}
    \begin{enumerate}[leftmargin=0.5cm] \itemsep -2pt %reduce space between items
        \item Techniques to deploy an application as a cloud computing service {\sl US Patent 10635437}
        \item System and method for cloud-based analytics {\sl US Patent 10637846}
        \item Testing an application in a production infrastructure temporarily provided by a cloud computing environment {\sl US Patent 10223242}
        \item Testing an application in a production infrastructure temporarily provided by a cloud computing environment (addendum) {\sl US Patent 10394696}
    \end{enumerate}


    \section{Experience} {\sl Senior Manager, Software Engineering } \hfill 2015 -- current \\
    Capital One Home Loans \& Auto Finance Data Engineering, Plano, TX
    \begin{itemize} \itemsep -2pt %reduce space between items
        \item Hiring, mentoring and performance management of an amazing data engineering division.
        \item Driving customer focus, engineering excellence and cost efficiency across org.
        \item Responsible for the Capital One fast data platform.
        \item Data platform implemented with microservices in Go lang, Cassandra, Mesos, Kafka, other open source and home grown solutions.
        \item Empowered business with realtime operational and risk metrics.
        \item Implemented data products ecosystem using open source (Jupyter Notebooks, Apache Airflow), home grown applications and vendor tools to help data analysts and data scientists derive meaningful insights.
        \item Presented in AWS:ReInvent 2019 and Tableau Conference 2019.
    \end{itemize}

    {\sl Senior Consultant, Data Engineering} \hfill            2012 -- 2015 \\
    Comcast Cable, Philadelphia, PA
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Managed onsite and offshore data engineering teams
        \item Implemented big data pipeline to analyze logs from millions of set-top boxes in AWS
        \item Enabled business to gather realtime intelligence from production and drive customer satisfaction
    \end{itemize}
    {\sl Senior Design \& Develpment Engineer/Specialist Engineer} \hfill        2006 -- 2012 \\
    Tata Elxsi Ltd, India
    \begin{itemize}
        \item Leading development teams working on multiple embedded R\&D projects
        \item Worked on embedded softwares for phones (J2ME), Android Set-top boxes and OCAP/MHP specifications
    \end{itemize}

    \section{Certifications}
    AWS Certified Solutions Architect - Associate -- Feb 2018\\
    Sun Certified Java Professional (Sun Microsystems) -- Jul 2008


\end{resume}
\end{document}




